Glacial flows, simulated faster

### 2023-06-06 talk-iu/slides.tex
I think this is a complete talk ... but I need to practice

%\subtitle{\emph{x}}

@@

%\titlegraphic{\begin{picture}(0,0)
%    \put(0,180){\makebox(0,0)[rt]{\includegraphics[width=4cm]{figs/software.png}}}
%  \end{picture}
%}

@@

%% to start section counter at 0 see
%% https://tex.stackexchange.com/questions/170222/change-the-numbering-in-beamers-table-of-content

@@

%\begin{frame}
%  \maketitle
%\end{frame}

@@

\begin{itemize}
\item FIXME
\item direct attack on the problem seems to require a \alert{multilevel} solver for \alert{variational inequalities} (VIs)
\item but in the non-local residual case this seems not to exist
    \begin{itemize}
    \item[$\circ$] the \alert{smoother} must reduce a residual formed from surface-motion term $\Phi(s) = - \bu|_s\cdot \bn_s$ (from a scalable Stokes solver)
    \end{itemize}
\item near-optimal multilevel solvers exist for simpler VI problems
\end{itemize}
\end{frame}

>>>>

%\subtitle{}

@@

@@

@@

@@

\begin{itemize}
\item direct attack on the NCP-coupled-to-Stokes problem, to get an optimal ($\beta=0$) solver, seems to require a \alert{multilevel} solver for \alert{variational inequalities} (VIs)
\item but in the \alert{non-local residual} case
    \begin{itemize}
    \item[$\circ$] application of the smoother needs to reduce the NCP residual from the surface-motion term $\Phi(s) = - \bu|_s\cdot \bn_s$, where $\bu|_s$ is evaluated from a scalable Stokes solver
    \end{itemize}
\item this seems not to exist, but we are starting to work on it \dots
\end{itemize}
\end{frame}

\begin{frame}{a \emph{new} multilevel SIA solver (joint with P.~Farrell)}

\begin{block}{FASCD}
\emph{full approximation storage constraint decomposition}

a multilevel method for box constrained NCPs and VIs
\end{block}

\begin{itemize}
\item in preparation, but here are fresh preliminary results \dots
\end{itemize}

\medskip
\begin{center}
\includegraphics[height=0.55\textheight]{../images/siabumps.png}
\end{center}
\end{frame}

\begin{frame}{a \emph{new} multilevel SIA solver (joint with P.~Farrell)}

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item results below show FASCD F-cycles give optimal ($\beta=0$) performance for the SIA problem
    \begin{itemize}
    \item[$\circ$] \emph{iterations} counts number of V-cycles after F-cycle ``ramp''
    \item[$\circ$] \emph{time} is for 4 core runs on my laptop
    \end{itemize}
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\hfill \input{fullcycle.tex}
\end{column}
\end{columns}

\bigskip
\begin{center}
\begin{tabular}{c|r|c|r}
\emph{levels} & $N$ & \emph{iterations} & \emph{time} (s) \\ \hline
\input{siaresults.txt} \hspace{-2.2mm}
\end{tabular}
\end{center}
\end{frame}
